The Astropy Project

### 2017-11-21 main.tex

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits.
The commit distribution \inlinecomment{Tom R}{too vague, maybe 'the distribution of number of commits as a function of ...'} follows an approximate power-law (with log-slope of
$\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
relatively small fraction of the contributor pool.
Roughly half of the commits were contributed by the top $4$
contributors, while $\sim 90$ percent of the commits came from the top $24$
contributors.

>>>>

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits. We can construct a distribution of the number of commits
per contributor ordered by decreasing number of commits. When doing this,
we find that this distribution
follows an approximate power-law (with log-slope of
$\approx -0.5$), meaning most of the commits were and are contributed by a
relatively small fraction of the contributor pool.
Roughly half of the commits were contributed by the top $4$
contributors, while $\sim 90$ percent of the commits came from the top $24$
contributors.
